---
title: "Homework_W6"
author:  "Carolina Melendez Declet"
format: html
---

10/6/2025 

Hello! This is my Quarto document for my **Week 6** homework. 

Goals for this homework:

- Create a table
- Create a plot

## Load Libraries 
```{r}
library(tidyverse) 
library(here)
library(kableExtra)
```

This loads the libraries I need to use for my analysis. 

## Load Data 
```{r}
ChemData <- read_csv(here("Week_06","Data","chemicaldata_maunalua.csv"))

view(ChemData)
```
This imports my dataset into R. This dataset is **seawater** samples for *water quality analysis*. 

## Cleanup Dataset 
```{r}
ChemData_clean <- ChemData |>
  drop_na() |> # removes all rows containing an NA
  separate_wider_delim(
    cols = Tide_time,
    delim = "_",
    names = c("Tide", "Time"),
    cols_remove = FALSE) |>
  mutate(Site_Zone = paste(Site, Zone, sep = ".")) # combines Site and Zone into one column

view(ChemData_clean)

```

This code is from my **Week 4** homework. Since I'm using the same dataset again, I'm just fixing my data again. 

## Filtering a Subset

```{r}
ChemData_HighTide <- ChemData_clean |>
  filter(Tide == "High")

view(ChemData_HighTide)
```

Filtered the data, so I can work with the **high tide** data only. Again, this code is also from my **Week 4** homework. 

## Plotting pH Data 
```{r}
#| label: fig-high-tide-ph
#| fig-cap: "pH measurements in seawater samples during high tide"
#| fig-width: 7
#| fig-height: 4


ChemData_HighTide_pH <- ggplot(data = ChemData_HighTide, mapping = aes(x = Site_Zone,y = pH,color = Site_Zone)) +
  geom_jitter(width = 0.12,height = 0,size = 1.5,alpha = 0.7) +
  labs(x = "Site and Zone", y = "pH", color = "Site and Zone") +
  scale_color_manual(values = c("#67001f", "#b2182b", "#d6604d", "#f4a582","#4393c3", "#2166ac", "#053061")) +
  theme_classic()

ChemData_HighTide_pH

ggsave(here("Week_06", "Outputs", "Week6HomeworkPlot.png"),
       width = 7,
       height = 4)
```

@fig-high-tide-ph shows the pH values across different sites during high tide. My plot is in my outputs folder! 


## Creating a Table 

```{r}
#| label: tbl-high-tide-ph
#| tbl-cap: "Mean pH across sites during high tide."


ChemData_HighTide |>
  group_by(Site_Zone) |>
  summarise(pH_mean = mean(pH, na.rm = TRUE)) |>
  kbl() |>
  kable_classic() |>
  row_spec(c(2, 4, 6), bold = TRUE, color = "white", background = "green") |> # highlight every other row, just for fun
  kable_styling(full_width = FALSE) 
```


Mean pH across sites during high tide are summarized in @tbl-high-tide-ph. 

## Open Access 

My homework is published here *https://01a112ec-8321-f9d8-3175-57f672955411.share.connect.posit.cloud/*
